Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-07-09 Documents/Paper/ms.tex
Fixed slight mistake

We model each galaxy as a mixture of two concentric elliptical galaxies, with
the following eight parameters. Firstly, two
parameters $x_c$ and $y_c$ describe the central position of the galaxy within
the image. The flux $f$ describes the total integral of the galaxy's
intensity profile. The axis ratio $q$ describes the ellipticity of the galaxy
and $\theta$ its orientation angle with respect to horizontal. Finally
we include a ``radius ratio'' $u$ describing the ratio of the radius of the
smaller gaussian with respect to that of the bigger gaussian, and a parameter
$v$ describing the fraction of the total flux in the outer gaussian
(therefore the fraction of the light in the smaller gaussian is $1-f$).

>>>>

We model each galaxy as a mixture of two concentric elliptical galaxies, with
the following eight parameters. Firstly, two
parameters $x_c$ and $y_c$ describe the central position of the galaxy within
the image. The flux $f$ describes the total integral of the galaxy's
intensity profile. The axis ratio $q$ describes the ellipticity of the galaxy
and $\theta$ its orientation angle with respect to horizontal. Finally
we include a ``radius ratio'' $u$ describing the ratio of the radius of the
smaller gaussian with respect to that of the bigger gaussian, and a parameter
$v$ describing the fraction of the total flux in the outer gaussian
(therefore the fraction of the light in the smaller gaussian is $1-v$).
